IOIs Analysis: The Sound of Teaching Music 2

### 2020-03-26 script/RNotebook/ioi_3.Rmd

##### Description: This is a summary of all analyses for a tempo (IOIs).
  - data <- data_ioi_3.csv

@@

#### Plot
- Error bars show SEM of the mean
- A dashed line represents the ideal tempo

@@

@@

#### Statistics
##### Normality check
```{r normality2, echo = FALSE}
ioi_art_ch_norm <- by(ioi_art_ch$Mean, list(ioi_art_ch$Condition, ioi_art_ch$Boundary), shapiro.test)
print(ioi_art_ch_norm)
```

##### Two-way ANOVA (ez)
```{r stats3, echo = FALSE}
ioi_art_ch_aov <- ezANOVA(
  data = df_ioi_art
  , dv = .(normIOI)
  , wid = .(SubNr)
  , within = .(Condition, Boundary)
  , type = 3
  , detailed = TRUE
)
ioi_art_ch_aov$ANOVA$F <- round(ioi_art_ch_aov$ANOVA$F, 4)
ioi_art_ch_aov$ANOVA$p <- round(ioi_art_ch_aov$ANOVA$p, 4)
print(ioi_art_ch_aov$ANOVA)
```

##### Two-way ANOVA (aov)
```{r stats4, echo = FALSE}
ioi_art_ch_aov_2 <- aov(Mean ~ Condition*Boundary + Error(SubNr/(Condition*Boundary)), data = ioi_art_ch)
print(summary(ioi_art_ch_aov_2))
```

@@

#### Plot
##### Line graph
- A dashed line represents the ideal tempo

@@

#### Plot
##### Line graph
- Error bars show SEM of the mean

@@

##### Box plot
- A dashed line represents the tempo given by a metronome (80bpm)

@@

#### Statistics
##### Normality check
```{r normality5, echo = FALSE}
ioi_dyn_ch_norm <- by(ioi_dyn_ch$Mean, list(ioi_dyn_ch$Condition, ioi_dyn_ch$Boundary), shapiro.test)
print(ioi_dyn_ch_norm)
```
  - Violate the normality assumption

##### Two-way ANOVA (ez)
```{r stats9, echo = FALSE}
ioi_dyn_ch_aov <- ezANOVA(
  data = df_ioi_dyn
  , dv = .(IOI)
  , wid = .(SubNr)
  , within = .(Condition, Boundary)
  , type = 3
  , detailed = TRUE
)
ioi_dyn_ch_aov$ANOVA$F <- round(ioi_dyn_ch_aov$ANOVA$F, 4)
ioi_dyn_ch_aov$ANOVA$p <- round(ioi_dyn_ch_aov$ANOVA$p, 4)
print(ioi_dyn_ch_aov)
```

##### Two-way ANOVA (aov)
```{r stats10, echo = FALSE}
ioi_dyn_ch_aov_2 <- aov(Mean ~ Condition*Boundary + Error(SubNr/(Condition*Boundary)), data = ioi_dyn_ch)
print(summary(ioi_dyn_ch_aov_2))
```

@@

## Sequence plot
#### Articulation{#sequence_art}
```{r seq_art, fig.width = 6, fig.height = 2, echo = FALSE}
# For each individual
ioi_art_seq <- aggregate(normIOI~SubNr*Condition*Skill*Interval, data = df_ioi_art,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_art_seq <- cbind(ioi_art_seq[,1:4], as.data.frame(ioi_art_seq[,5]))
# Change colnames
colnames(ioi_art_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")

@@

#### Dynamics{#sequence_dyn}
```{r seq_dyn, fig.width = 6, fig.height = 2, echo = FALSE}
# For each individual
ioi_dyn_seq <- aggregate(normIOI~SubNr*Condition*Skill*Interval, data = df_ioi_dyn,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_dyn_seq <- cbind(ioi_dyn_seq[,1:4], as.data.frame(ioi_dyn_seq[,5]))
# Change colnames
colnames(ioi_dyn_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")

>>>>

Description: This is a summary of all analyses for a tempo (IOIs).
  - data <- data_ioi_3.csv

- Last checked: 19/03/20

# Outline - Interonset intervals (IOIs)
## [Experimental Design](#design)

## [Articulation](#ioi-articulation)

- Individual results
  + [All](#art_ind_all)
  + [Phrase bondaries](#art_ind_phrase)
  + [Trial by trial](#art_ind_trial)
  + [Variability](#art_ind_var_all)
  + [Variability trial-by-trial](#art_ind_var_trial)

- Group results and stats (if available)
  + [All](#art_group_all)
  + [Phrase bondaries](#art_group_phrase)
  + [Trial by trial](#art_group_trial)
  + [Variability](#art_group_var_all)
  + [Variability trial-by-trial](#art_group_var_trial)

- [Sequence plot](#sequence_art)

## [Dynamics](#ioi-dynamics)

- Individual results
  + [All](#dyn_ind_all)
  + [Phrase bondaries](#dyn_ind_phrase)
  + [Trial by trial](#dyn_ind_trial)
  + [Variability all](#dyn_ind_var_all)
  + [Variability trial-by-trial](#dyn_ind_var_trial)

- Group results and stats (if available)
  + [All](#dyn_group_all)
  + [Phrase bondaries](#dyn_group_phrase)
  + [Trial by trial](#dyn_group_trial)
  + [Variability all](#dyn_group_var_all)
  + [Variability trial-by-trial](#dyn_group_var_trial)

- [Sequence plot](#sequence_dyn)

@@

### Plot
#### Bar graph
- Error bars show SEM of the mean
- A dashed line represents the ideal tempo

@@

#### Box plot
- A dashed line represents the ideal tempo

@@

### Statistics
#### Normality check
```{r normality2, echo = FALSE}
ioi_art_ch_norm <- by(ioi_art_ch$Mean, list(ioi_art_ch$Condition, ioi_art_ch$Boundary), shapiro.test)
print(ioi_art_ch_norm)
```

#### Two-way ANOVA (ez)
```{r stats3, echo = FALSE}
ioi_art_ch_aov <- ezANOVA(
  data = df_ioi_art
  , dv = .(normIOI)
  , wid = .(SubNr)
  , within = .(Condition, Boundary)
  , type = 3
  , detailed = TRUE
)
ioi_art_ch_aov$ANOVA$F <- round(ioi_art_ch_aov$ANOVA$F, 4)
ioi_art_ch_aov$ANOVA$p <- round(ioi_art_ch_aov$ANOVA$p, 4)
print(ioi_art_ch_aov$ANOVA)
```

#### Two-way ANOVA (aov)
```{r stats4, echo = FALSE}
ioi_art_ch_aov_2 <- aov(Mean ~ Condition*Boundary + Error(SubNr/(Condition*Boundary)), data = ioi_art_ch)
print(summary(ioi_art_ch_aov_2))
```

@@

#### Plot
#### Line graph
- A dashed line represents the ideal tempo

@@

#### Plot
##### Line graph
- Error bars show SEM of the mean
- A dashed line represents the ideal tempo

@@

#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm)

@@

### Statistics
#### Normality check
```{r normality5, echo = FALSE}
ioi_dyn_ch_norm <- by(ioi_dyn_ch$Mean, list(ioi_dyn_ch$Condition, ioi_dyn_ch$Boundary), shapiro.test)
print(ioi_dyn_ch_norm)
```
  - Violate the normality assumption

#### Two-way ANOVA (ez)
```{r stats9, echo = FALSE}
ioi_dyn_ch_aov <- ezANOVA(
  data = df_ioi_dyn
  , dv = .(IOI)
  , wid = .(SubNr)
  , within = .(Condition, Boundary)
  , type = 3
  , detailed = TRUE
)
ioi_dyn_ch_aov$ANOVA$F <- round(ioi_dyn_ch_aov$ANOVA$F, 4)
ioi_dyn_ch_aov$ANOVA$p <- round(ioi_dyn_ch_aov$ANOVA$p, 4)
print(ioi_dyn_ch_aov)
```

#### Two-way ANOVA (aov)
```{r stats10, echo = FALSE}
ioi_dyn_ch_aov_2 <- aov(Mean ~ Condition*Boundary + Error(SubNr/(Condition*Boundary)), data = ioi_dyn_ch)
print(summary(ioi_dyn_ch_aov_2))
```

@@

## Sequence plot
### Articulation{#sequence_art}
```{r seq_art, fig.width = 10, fig.height = 2, echo = FALSE}
# For each individual
ioi_art_seq <- aggregate(normIOI~SubNr*Condition*Skill*Interval, data = df_ioi_art,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_art_seq <- cbind(ioi_art_seq[,1:4], as.data.frame(ioi_art_seq[,5]))
# Change colnames
colnames(ioi_art_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")

@@

### Dynamics{#sequence_dyn}
```{r seq_dyn, fig.width = 10, fig.height = 2, echo = FALSE}
# For each individual
ioi_dyn_seq <- aggregate(normIOI~SubNr*Condition*Skill*Interval, data = df_ioi_dyn,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_dyn_seq <- cbind(ioi_dyn_seq[,1:4], as.data.frame(ioi_dyn_seq[,5]))
# Change colnames
colnames(ioi_dyn_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")
